3_Explore_Missingness

### 2017-01-22 Code/3_Explore_Missingness.Rmd

**Figure 1: Proportion missing by State (panel) and Age group (x-axis), ordered by increasing size of black population in 2013**
```{r bystate, fig.width = 12, fig.height = 37, echo=F}
bystate <- 
  dat %>%
  group_by(State2, Race2, Age2) %>%
  summarise(prop.missing = mean(is.na(Count)))

>>>>

**Figure 1: Proportion missing by State (panel) and Age group (x-axis), ordered by increasing size of black population in 2013**
```{r bystate, fig.width = 12, fig.height = 37, echo=F}
bystate <- 
  dat %>%
  group_by(state, race, age) %>%
  summarise(prop.missing = mean(is.na(deaths)))
